Replication of Brydevall et al. 2018

### 2023-02-28 219-2023-analysis/manuscript.qmd
use osf to get data
add osfr as dependency

library(dplyr)
library(ggplot2)
library(readr)
library(ez)
```

>>>>

library(dplyr)
library(ggplot2)
library(readr)
library(ez)
library(osfr)
```

```{r}
#| label: Get preprocessed data from OSF
#| include: false
#| echo: false

osf_retrieve_node("2pxf4") %>%
  osf_ls_files() %>%
  osf_download(path="data/preprocessed/", conflicts="skip")
```
